Weekly Paragraphs

### 2012-11-02 latex/paragraphs.tex
shitty paragraphs

>>>>

\section{November 2, 2012}
Initial Approaches

We modelled a single slice of neural tissue with a finite Gaussian mixture model with full covariances. The feature vector $(x, y, i)$ consisted of the positional coordinates and pixel intensity. Each cluster represented the pixels belonging to a single cell, with a special background cluster to contain cell membrance and interstitial space. For this background, we experimented with both a triangular probability density $p(i) = 2 - 2*i$ and a sigmoid density of the form $p(i) = \frac{1}{Z} \left[ 1 - \left( 1 + \exp(-p(i-c)) \right)^-1 \right]$ with $p$ and $c$ denoting the precision (inverse scale) and location (the preimage of the midpoint of the range). Inference was performed with Gibbs sampling.

Visually, our segmentation seems reasonable, although cells whose interior intensity varies significantly tend to be oversegmented, and the cell boundary model is insufficient because the boundary intensity varies locally (see slides). A more accurate background model must be adaptive.

A more serious problem is that our Gaussian intensity model is insufficienltly compact: the standard deviations are far too high to accurately model the bounded $[0, 1]$ intensity range. To rectify this, we experimented with modelling the third dimension as a Beta distribution independently of the first two dimensions, but still dependent on class labels. We implemented a Metropolis-Hastings sampler using a lognormal proposal and a prior based on \cite{Bouguila2006}. We modified the prior to take the form $$ \left[ 1 - exp(-( (s - 0.5)^2)) (1 - exp(-( (a - 1)^2)))(1 - exp(-( (b - 1).^2))) (1 - exp(-d * ((s - 2).^2 + (m - 0.5).^2))) exp(-r / (s.^2 .* m .* (1 - m)) - (k * s.^2) / 2) \right]$$. This avoids distributions with $a, b < 1$, which lead to unbounded U-shaped distributions, as well as $a = b = 1$, the uniform distribution. Unfortunately, our experiment with this model reverted to axis-aligned decision boundaries. It appears that spatio-intensity correlations are essential.
